Minimizing post-shock forecasting error through aggregation of outside information

### 2021-02-06 Revision/letter.tex
added letter

We are excited to submit our manuscript ``Minimizing post-shock forecasting error through aggregation of outside information'' for possible publication at the International Journal of Forecasting.

In this manuscript, we  develop forecasting methodology for providing credible forecasts for time series that are known to have undergone a recent shock for which no post-shock data is observed. Our methodology has various potential real-life applications in many forecasting settings.

We construct credible forecasts by borrowing knowledge from other time series that have undergone similar shocks for which post-shock outcomes are observed. We propose risk-reduction propositions that provide conditions that establish when our methodology works. Bootstrap and leave-one-out cross validation procedures are provided to prospectively evaluate the performance of our methodology.

We demonstrate the utility of our methodology with a real data analysis involving the forecasting of Conoco Phillips stock price during a time period of massive oil price volatility and increasing COVID-19 panic. We also provide several numerical examples that demonstrate the effectiveness of our prospective evaluation procedures.

We confirm that this manuscript is only under consideration at the International Journal of Forecasting. Thank you for your consideration.

>>>>

We are grateful to submit a revision for our manuscript ``Minimizing post-shock forecasting error through aggregation of outside information'' at International Journal of Forecasting.  The responses to all of the comments are included in the resubmission files.

Thank you for your reconsideration.
